Modeling the Latent Space of Symbolic String Quartet Music

### 2021-06-07 papers/final/alex/paper.tex
add gdrive outputs links

%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf,authorversion]{acmart}
\usepackage{pgf}
\usepackage{pgfplots}
%% NOTE that a single column version may be required for
%% submission and peer review. This can be done by changing
%% the \doucmentclass[...]{acmart} in this template to
%% \documentclass[manuscript,screen,review]{acmart}
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

@@

\begin{abstract}
  This paper presents the results of a project to apply a recurrent
  variational autoencoder to the task of modeling a latent space for
  generating pieces of multi-instrument symbolic classical music
  through interpolation.
\end{abstract}

@@

A collection of several samples of the autoencoded outputs and
interpolations, is presented at:
\href{https://drive.google.com/drive/folders/12o04uubXtP8WdI62Xe5fjE6wQgzCPG8n?usp=sharing
  (Google Drive link)}

>>>>

%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf,authorversion]{acmart}
\usepackage{pgf}
\usepackage{pgfplots}
\usepackage{url}
%% NOTE that a single column version may be required for
%% submission and peer review. This can be done by changing
%% the \doucmentclass[...]{acmart} in this template to
%% \documentclass[manuscript,screen,review]{acmart}
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

@@

\begin{abstract}
  This paper presents the results of a project to apply a recurrent
  variational autoencoder to the task of modeling a latent space for
  generating pieces of multi-instrument symbolic classical music
  through interpolation. The code utilized for this research is available at:
  \url{https://github.com/jackPhn/CSS586_Project/}
\end{abstract}

@@

A collection of samples of the autoencoded outputs and
interpolations, converted to mp3 format, is presented at:
\url{https://drive.google.com/drive/folders/1SlQOI_cL452PftO3KmOYO_qglE2RotCX?usp=sharing}.
Each of the 18 directories contains five interpolations between two of
the string quartet pieces in the MusicNet corpus, numbered 0-4.
